---
title: "PFL DATA REPORT"
format: 
  docx:
    reference-doc: 'C:/Users/milena.singletary/OneDrive - BOA Technology Inc/General - PFL Team/Testing Segments/Report_Template.docx'
editor: visual
editor_options: 
  chunk_output_type: console
execute: 
  error: true
  warning: false
---

# CONFIDENTAL CONTENT FOR BOA EMPLOYEES ONLY. PLEASE CONTACT PFL DIRECTLY WITH ANY QUESTIONS.

+--------------------+-----------------------------------------------------+
| Test Name          | 2025_Performance_HighCutPFSWorkwearII_TimberlandPro |
+====================+=====================================================+
| **Segment:**       | Workwear                                            |
+--------------------+-----------------------------------------------------+
| **Date:**          | June 2025                                           |
+--------------------+-----------------------------------------------------+
| **Test Type:**     | Mechanistic                                         |
+--------------------+-----------------------------------------------------+
| **Configurations** | Baseline: CFS (Classic Fit Solution)                |
|                    |                                                     |
|                    | Test configurations:                                |
|                    |                                                     |
|                    | -   PFS                                             |
|                    |                                                     |
|                    | -   PFSDZ (PFS Dual Zone)                           |
+--------------------+-----------------------------------------------------+

# Purpose & Background

-   Previous learning's have showed imporved heel hold and ankle stability when testing zonal fit of midcut boots.

-   With more robust uppers in workwear and more so in high cut work boots, do these learning still hold true?

-   **The purpose of this test was to evaluate the effects of zonal PFS on a high cut boot with a robust upper.**

# Hypothesis

**Key Benefits:**

H1: PFSL will improve heel hold by wrapping the midfoot best. Heel hold will be measured as contact area between the heel and the midsole during walking. The heel hold will be evaluated during indoor trail walking and uphill, and downhill treadmill walking.

H2: The PFSC will improve ankle stability by providing improved fit around the ankle. Ankle stability will be measured as the peak eversion velocity during trail walking and peak eversion ankle moment during weighted lunges.

**Additional Benefits:**

H3: The heel lock will improve running speed with no change in heart rate. The dual dial will provide the most improvement.

# Methods

+--------------+---------------------------------------+---------------------------------------+----------------------------+
| Subjects     | Movements                             | Equipment                             | Measurements               |
+==============+=======================================+=======================================+============================+
| 11 Athletes  | Uneven terrain walking                | -   Pressure insoles                  | Enduundefinedrance:        |
|              |                                       |                                       |                            |
| -   10 Male  |                                       | -   Inertial Measurement Units (IMUs) | -   Walking Speed          |
|              |                                       |                                       | -   Peak Toe Pressure      |
| -   1 Female |                                       |                                       | -   Center of Mass Work    |
|              |                                       |                                       |                            |
|              |                                       |                                       | Fit:                       |
|              |                                       |                                       |                            |
|              |                                       |                                       | -   Heel contact area      |
|              |                                       |                                       | -   Peak eversion velocity |
+--------------+---------------------------------------+---------------------------------------+----------------------------+
|              | Single Leg Landings on uneven terrain | -   Pressure insoles                  | Stability & Control:       |
|              |                                       |                                       |                            |
|              |                                       |                                       | -   Time-to-stabilize      |
+--------------+---------------------------------------+---------------------------------------+----------------------------+
|              | Weighted Lunge to Stand               | -   In-ground force plates            | Endurance:                 |
|              |                                       |                                       |                            |
|              |                                       | -   Motion Capture cameras            | -   Ankle eversion moment  |
|              |                                       |                                       |                            |
|              |                                       |                                       | -   Knee abduction moment  |
+--------------+---------------------------------------+---------------------------------------+----------------------------+

# Configurations

+--------------------------------------+---------------+-----------------------+
| Baseline: Classic Fit Solution (CFS) | PFS (PFS)     | PFS Dual Zone (PFSDZ) |
+======================================+===============+=======================+
|                                      |               |                       |
+--------------------------------------+---------------+-----------------------+

```{r}
#| echo: false
#| warning: false
#| include: false


library(readxl)
library(tidyverse)
library(lme4)
library(emmeans)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(wordcloud)
library(readxl)
library(brms)
library(patchwork)
library(tidyr)
library(fmsb)
library(gt)
rm(list=ls())
```

```{r}
#| echo: false
#| warning: false

#Load in Compiled Qualitative Sheet
qualDat <- read_xlsx('C:\\Users\\milena.singletary\\OneDrive - BOA Technology Inc\\General - PFL Team\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorwearII_TimberlandPro\\CompiledQualData_HighCutWWII.xlsx')


# Pressure from Trail Walking
PressWalkDat <- read.csv('Z:\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorkwearII_TimberlandPro\\Xsensor\\cropped\\1_CompiledResults.csv')

# Load in the overground lunge data
SUDat <- read.csv('Z:\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorkwearII_TimberlandPro\\overground\\1_StandUp.csv')

# Load in the trail landing data
UnLandDat <- read.csv('Z:\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorkwearII_TimberlandPro\\Xsensor\\cropped\\1_CompiledResults_SLL.csv')

# Load in the IMU data
IMUdat <- read.csv('Z:\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorkwearII_TimberlandPro\\IMU\\0_Trail_CompIMUmetrics.csv')


TreadDat <-  read.csv('Z:\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorkwearII_TimberlandPro\\treadmill\\0_TreadmillOutcomes_1.csv')
  
staticPress <- read.csv('Z:\\Testing Segments\\WorkWear_Performance\\2025_Performance_HighCutPFSWorkwearII_TimberlandPro\\Xsensor\\static\\1_CompiledResults_Static.csv')


baseline <- 'CFS' # baseline configuration

otherConfigs <- c('PFS', 'PFSDZ') # other configurations tested against base
allConfigs <- c(baseline, otherConfigs)

qualDat$Config <- factor(qualDat$Config, allConfigs)

PressWalkDat <- as_tibble(PressWalkDat) # creating the data frame
PressWalkDat$Config <- factor(PressWalkDat$Config, allConfigs)

SUDat <- as_tibble(SUDat) # creating the data frame
SUDat$Config <- factor(SUDat$Config, allConfigs)

UnLandDat <- as_tibble(UnLandDat) # creating the data frame
UnLandDat$Config <- factor(UnLandDat$Config, allConfigs)

IMUdat <- as_tibble(IMUdat) # creating the data frame
IMUdat$Config <- factor(IMUdat$Config, allConfigs)


TreadDat <- as_tibble(TreadDat)
TreadDat$Config <- factor(TreadDat$Config, allConfigs)

staticPress <- as_tibble(staticPress)
staticPress$Config <- factor(staticPress$Config, allConfigs)


# updated withinAvg plot 
withinSubPlotAvg <- function(inputDF, colName, dir = 'lower', yLabel = NULL) {
  # Validate the `dir` input
  if(!dir %in% c('lower', 'higher')){
    stop("The 'dir' argument must be either 'lower' or 'higher'.")
  }
  # Calculate the mean for each Subject and Config, removing NA values
  meanDat <- inputDF %>%
    group_by(Subject, Config) %>%
    summarize(mean = mean(!! sym(colName), na.rm = TRUE), .groups = 'drop')
  # Determine the best configuration based on the direction
  if (dir == 'lower'){
    whichConfig <- meanDat %>%
      group_by(Subject) %>%
      reframe(BestConfig = Config[which.min(mean)])
  } else if (dir == 'higher') {
    whichConfig <- meanDat %>%
      group_by(Subject) %>%
      reframe(BestConfig = Config[which.max(mean)])
  }
  # Rename BestConfig to Config for merging
  whichConfig <- whichConfig %>%
    rename(Config = BestConfig)
  # Merge the best configuration back to the mean data
  mergedData <- merge(meanDat, whichConfig, by = c("Subject", "Config"))
  # Calculate overall mean for each Config, removing NA values
  overallMean <- meanDat %>%
    group_by(Config) %>%
    summarize(overallMean = mean(mean, na.rm = TRUE), .groups = 'drop')
  # Plotting with ggplot2
  plot <- ggplot() +
    geom_point(data = meanDat, mapping = aes(x = as.factor(Config), y = mean, group = Subject, color = 'Subject Means'), size = 3, alpha = 0.5) +
    geom_line(data = meanDat, mapping = aes(x = as.factor(Config), y = mean, group = Subject, color = 'Subject Means'), alpha = 0.5) +
    geom_point(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, color = 'Overall Mean'), size = 4, shape = 17) +
    geom_line(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, group = 1, color = 'Overall Mean'), size = 1.5) +
    scale_color_manual(values = c('Subject Means' = 'grey', 'Overall Mean' = '#003C4C')) +
    xlab('Configuration') +
    theme(text = element_text(size = 16), legend.title = element_blank())
  # Set y-axis label
  if (!is.null(yLabel)) {
    plot <- plot + ylab(yLabel)
  } else {
    plot <- plot + ylab(paste0(colName))
  }
  print(plot)
}

extractVals <- function(dat, mod, configNames, baseConfig, var, dir) {
  
  Config = rep(NA, length(configNames))
  ProbImp = matrix(0, length(configNames))
  lowCI = matrix(0, length(configNames))
  highCI = matrix(0, length(configNames))
  
  for (i in 1:length(configNames)) {
    # This function takes the original dataframe (dat, same one entered into runmod), the Bayesian model from brms (runmod), 
    # the configuration Name, and the variable you are testing. It returns:
    # [1] the probabality the variable was better in the test config vs. the baseline config
    # [3] the lower bound of the bayesian 95% posterior interval (as percent change from baseline) 
    # [4] the upper bound of the bayesian 95% posterior interval (as percent change from baseline)
    #i = 1
    
    configName = configNames[i]
    configColName <- paste('b_Config', configName, sep = "")
    posterior <- posterior_samples(mod)
    
    if (dir == 'lower'){
      prob <- sum(posterior[,configColName] < 0) / length(posterior[,configColName])
      
    } else if (dir == 'higher') {
      
      prob <- sum(posterior[,configColName] > 0) / length(posterior[,configColName])
    }
    
    ci <- posterior_interval(mod, prob = 0.80)
    ciLow <- ci[configColName,1] 
    ciHigh <- ci[configColName,2]
    
    SDdat <- dat %>%
      group_by(Subject) %>%
      summarize(sd = sd(!! sym(var), na.rm = TRUE), mean = mean(!! sym(var), na.rm = TRUE))
    
    meanSD = mean(SDdat$sd , na.rm = TRUE)
    mean = mean(SDdat$mean, na.rm = TRUE)
    ci_LowPct <- meanSD*ciLow/mean*100
    ci_HighPct <- meanSD*ciHigh/mean*100
    
    output = list('Config:', configName, 'Probability of Improvement:', prob, 'Worse end of CI:', ci_LowPct, 'Best end of CI:', ci_HighPct)
    Config[i] = configName
    ProbImp[i] = prob
    lowCI[i] = ci_LowPct
    highCI[i] = ci_HighPct
  }
  ProbImp = round(ProbImp*100)
  lowCI = round(lowCI, 1)
  highCI = round(highCI,1)
  output = cbind(Config, ProbImp, lowCI, highCI)
  
  colnames(output) = c('Config', 'Probability of Improvement', 'Low end of CI', 'High end of CI')
  
  sentences = rep(NA, nrow(output))
  
  for (i in 1:nrow(output)){
    if (as.numeric(output[i,2]) >= 90){
      sentences[i] <- paste0('We have meaningful confidence that ',output[i,1], ' outperformed ', baseConfig, ' (',output[i,2], '%)', '\n', '\t', '- Estimated difference: ',output[i,3],' to ',output[i,4],'%' )
    } else if (as.numeric(output[i,2]) >= 80) {      
      sentences[i] <- paste('We have moderate confidence that',output[i,1], 'outperformed', baseConfig, '(',output[i,2], '%)','\n', '\t', '- Estimated difference:',output[i,3],'to',output[i,4],'%')
    } else if (as.numeric(output[i,2]) >= 70){
      sentences[i] <- paste('We have minimal confidence that',output[i,1], 'outperformed', baseConfig, '(',output[i,2], '%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
    } else if (as.numeric(output[i,2]) >= 30){
      sentences[i] <- paste('There were inconsistent differences between',output[i,1],'and',baseConfig,'(',output[i,2],'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
    } else if (as.numeric(output[i,2]) >= 20){
      sentences[i] <- paste('We have minimal confidence that',output[i,1],'performed worse than',baseConfig,'(',(100 - as.numeric(output[i,2])),'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
    } else if (as.numeric(output[i,2]) >= 10){
      sentences[i] <- paste('We have moderate confidence that',output[i,1],'performed worse than',baseConfig,'(',(100 - as.numeric(output[i,2])),'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
    } else {
      sentences[i] <- paste('We have meaningful confidence that',output[i,1],'performed worse than',baseConfig,'(',(100 - as.numeric(output[i,2])),'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
    }
  }
  
  writeLines(sentences)
  return()
}

# Setting up  "Best Of" line plots 
withinSubQualPlot <- function(inputDF) {
  
  # direction can be 'lower' or higher'. It is the direction of change that is better. 
  # For example, for contact time lower is better. so we put 'lower'. for jump height, higher is better, so we put higher. 
  
  whichConfig <- inputDF %>%
    group_by(Subject) %>%
    summarize(
      BestConfig = Config[which.max(OverallFit)]
    )
  
  whichConfig <- merge(inputDF, whichConfig)
  
  ggplot(data = whichConfig, mapping = aes(x = as.factor(Config), y = OverallFit, col = BestConfig, group = Subject)) + geom_point(size = 4) + 
    geom_line() + xlab('Configuration') + scale_color_manual(values=c("#000000", "#00966C", "#ECE81A","#DC582A","#CAF0E4")) + ylab('Rating') + theme(text = element_text(size = 16))
  
}

EffectSizeLM <- function(df, inputmodel) {
  myformula <- as.formula(paste0(inputmodel))
  full.mod = lmer(myformula, data = df, REML = TRUE, na.action = "na.omit")
  conditions.emm <- emmeans(full.mod, "Config", lmer.df = "satterthwaite")
  efsi_sum = summary(eff_size(conditions.emm, sigma = sigma(full.mod), edf = Inf))
  
  for (ii in 1:(length(unique(df$Config))-1)){
    print(paste('effect size for:', efsi_sum$contrast[ii], ' is ', round(efsi_sum$effect.size[ii],3)))
  }

return()
}

###############################
```

# Summary of Findings

(Did we achieve the goal of the study?)

# Next Steps

-   

# Recommendations

-   

# Key Benefit Performance

|                             | Base | Config1 | Config2 |
|-----------------------------|------|---------|---------|
| Power Transfer              | 50   |         |         |
| Energy Efficiency           | 50   |         |         |
| Stability & Control         | 50   |         |         |
| Quantitative Fit            | 50   |         |         |
| Overall Performance Ranking | 50   |         |         |

# Additional Benefit Performance

|                     | Base | Config1 | Config2 |
|---------------------|------|---------|---------|
| Qualitative Ranking | 90   |         |         |

# **Qualitative**

```{r}
#| echo: false
#| warning: false
#| include: true 
#| layout-ncol: 2  

qualDat %>%
  pivot_longer(cols = OverallFit:Cuff, 
               names_to = "Location", values_to = "Rating") %>%
  group_by(Location, Config) %>%
  summarize(
    medAvg = median(Rating, na.rm = TRUE)
  ) %>%
  gt()


#Defining the rating for the location 
#Density plots for fit ratings of shoe locations
qualDat <- pivot_longer(qualDat, cols = Forefoot:Cuff, names_to = 'Location', values_to = 'Rating')

FF <- qualDat %>% 
  filter(Location=="Forefoot")


qualDat$Location <- factor(qualDat$Location, c('Forefoot', 'Midfoot', 'Heel', 'Cuff')) 

```

```{r}
#| echo: false
#| warning: false
#| include: true

withinSubQualAvg(qualDat)
ggplot(qualDat, mapping = aes(x = Rating, fill = Config)) + 
  geom_histogram(position = 'dodge', binwidth = 1) + facet_wrap(~Location) + scale_fill_manual(values=c("#999999", "#00966C", "#ECE81A","#DC582A","#CAF0E4")) +
  ylab('Responses') + theme(text=element_text(size=20)) + geom_vline(xintercept = 5, linewidth = 1)
```

```{r}
#| echo: false
#| warning: false
#| include: false


# qual average plot
withinSubQualAvg <- function(inputDF) {
  
  # direction can be 'lower' or higher'. It is the direction of change that is better. 
  # For example, for contact time lower is better. so we put 'lower'. for jump height, higher is better, so we put higher. 
  # Calculate the mean for each Subject and Config, removing NA values
  meanDat <- inputDF %>%
    group_by(Subject, Config) %>%
    summarize(mean = mean(OverallFit, na.rm = TRUE), .groups = 'drop')
  
  
  whichConfig <- inputDF %>%
    group_by(Subject) %>%
    summarize(
      BestConfig = Config[which.max(OverallFit)]
    )
  
  whichConfig <- whichConfig %>%
    rename(Config = BestConfig)
  
  mergeDat <- merge(meanDat, whichConfig)
  
  overallMean <- meanDat %>%
    group_by(Config) %>%
    summarize(overallMean = mean(mean, na.rm = TRUE), .groups = 'drop')
  # Plotting with ggplot2
  plot <- ggplot() +
    geom_point(data = meanDat, mapping = aes(x = as.factor(Config), y = mean, group = Subject, color = 'Subject Means'), size = 3, alpha = 0.5) +
    geom_line(data = meanDat, mapping = aes(x = as.factor(Config), y = mean, group = Subject, color = 'Subject Means'), alpha = 0.5) +
    geom_point(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, color = 'Overall Mean'), size = 4, shape = 17) +
    geom_line(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, group = 1, color = 'Overall Mean'), linewidth = 1.5) +
    scale_color_manual(values = c('Subject Means' = 'grey', 'Overall Mean' = '#003C4C')) +
    xlab('Configuration') + ylab('Rating') +
    theme(text = element_text(size = 16), legend.title = element_blank()) 
    
  
  print(plot)
  
}

withinSubQualAvg(qualDat)
```

## **Dial Torque**

```{r}
#| echo: false
#| warning: false
#| include: true


qualDat %>%
  group_by(Config)%>%
  summarize(
    R_Torque_Cuff = mean(R_DialTorque2, na.rm = TRUE),
    R_Torque_Instep = mean(R_DialTorque1, na.rm = TRUE),
    L_Torque_Cuff = mean(L_DialTorque2, na.rm = TRUE),
    L_Torque_Instep = mean(L_DialTorque1, na.rm = TRUE)
  )%>%
  gt()

ggplot(qualDat, aes(x=Config, y = L_DialTorque1, color = Config, group= Subject)) + 
  geom_point(size = 4)+ 
  geom_line(aes(color=Config))+
  # facet_wrap(~Subject)+
  scale_color_manual(values=c("#000000","#00966C", "#ECE81A","#DC582A","#CAF0E4"))+ 
  theme(text = element_text(size = 16))+ 
  ylab('Instep Dial - Torque [N-cm]')+ 
  xlab('Config')+
  ggtitle('Left Foot')


withinSubPlotAvg(qualDat, colName ='R_DialTorque1', dir = 'higher')  + ylab('Instep Dial - Torque [N-cm]')

```

```{r}
#| echo: false
#| warning: false
#| include: true 

torqueDat <- qualDat %>%
  group_by(Subject) %>%
  mutate(z_score = scale(L_DialTorque1)) %>%
  group_by(Config)


torqueMod <- brm(data = torqueDat, # Bayes model
              family = gaussian,
              z_score ~  Config + (1  | Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


extractVals(torqueDat , torqueMod, otherConfigs, baseline, 'L_DialTorque1', 'higher')
```

# Energy Efficiency

## **Walking Speed (higher is better)** **- Uneven Terrain Walking**

```{r}
#| echo: false
#| warning: false
#| include: false
#| layout-ncol: 2  


###### Walking Speed

Speeddat <- IMUdat %>% 
  group_by(Subject) %>%
  filter(imuSpeed > 0.25) %>%
  mutate(z_score = scale(imuSpeed)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = Speeddat, aes(x = imuSpeed, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

Speeddat <- subset(Speeddat, Speeddat$z_score < 2) #removing outliers
Speeddat <- subset(Speeddat, Speeddat$z_score > -2)



# Note for trail run metrics: Warmup was reduced (from 1000 to 400)
SpeeddatMod <- brm(data = Speeddat, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 400, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)



```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(Speeddat, colName = 'imuSpeed', dir = 'higher')
p + ylab('Walking Speed (m/s)')


extractVals(Speeddat, SpeeddatMod, otherConfigs, baseline, 'imuSpeed', 'higher') 

EffectSizeLM(Speeddat,'imuSpeed ~ Config + (Config|Subject)')
```

## **Toe Clawing: Peak Toe Pressure (Lower is Better) - All Walking and Uneven Terrain Landings**

```{r}
#| echo: false
#| warning: false
#| include: false


###### Peak Toe Pressure Walking

PeakToeWalkdat <- PressWalkDat %>% 
  group_by(Subject) %>%
  mutate(z_score = scale(maxmaxToes)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = PeakToeWalkdat, aes(x = maxmaxToes, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

PeakToeWalkdat <- subset(PeakToeWalkdat, PeakToeWalkdat$z_score < 2)#removing outliers
PeakToeWalkdat <- subset(PeakToeWalkdat, PeakToeWalkdat$z_score > -2)



# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
PeakToeWalkdatMod <- brm(data = PeakToeWalkdat, # Bayes model
              family = gaussian,
              z_score ~ Config + Movement + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)




###### Peak Toe Pressure Trail Landings

PeakToeLanddat <- UnLandDat %>% 
  group_by(Subject) %>%
  mutate(z_score = scale(ToeClawPeak)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = PeakToeLanddat, aes(x = ToeClawPeak, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

PeakToeLanddat <- subset(PeakToeLanddat, PeakToeLanddat$z_score < 2)#removing outliers
PeakToeLanddat <- subset(PeakToeLanddat, PeakToeLanddat$z_score > -2)




# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
PeakToeLanddatMod <- brm(data = PeakToeLanddat, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(PeakToeWalkdat, colName = 'maxmaxToes', dir = 'lower')
p + ylab('Peak Toe Pressure (kPa)')


extractVals(PeakToeWalkdat, PeakToeWalkdatMod, otherConfigs, baseline, 'maxmaxToes', 'lower')


```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 


p <- withinSubPlotAvg(PeakToeLanddat, colName = 'ToeClawPeak', dir = 'lower')
p + ylab('Peak Toe Pressure (kPa)')

extractVals(PeakToeLanddat, PeakToeLanddatMod, otherConfigs, baseline, 'ToeClawPeak', 'lower')
```

## Peak Toe Pressure Walking: UH, DH, Trail

```{r}
#| echo: false
#| warning: false
#| include: false

###### Peak Toe Pressure UH 

PeakToeUH <- PressWalkDat %>% 
  group_by(Subject) %>%
  filter(Movement == 'uh')%>%
  mutate(z_score = scale(maxmaxToes)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = PeakToeUH, aes(x = maxmaxToes, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

PeakToeUH <- subset(PeakToeUH, PeakToeUH$z_score < 2)#removing outliers
PeakToeUH <- subset(PeakToeUH, PeakToeUH$z_score > -2)



# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
PeakToeUHMod <- brm(data = PeakToeUH, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


####### downhill

PeakToeDH <- PressWalkDat %>% 
  group_by(Subject) %>%
  filter(Movement == 'dh')%>%
  mutate(z_score = scale(maxmaxToes)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = PeakToeDH, aes(x = maxmaxToes, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

PeakToeDH <- subset(PeakToeDH, PeakToeDH$z_score < 2)#removing outliers
PeakToeDH <- subset(PeakToeDH, PeakToeDH$z_score > -2)



# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
PeakToeDHMod <- brm(data = PeakToeDH, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)



##### trail
PeakToeTr <- PressWalkDat %>% 
  group_by(Subject) %>%
  filter(Movement == 'trail' | Movement == 'trailwalk')%>%
  mutate(z_score = scale(maxmaxToes)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = PeakToeTr, aes(x = maxmaxToes, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

PeakToeTr <- subset(PeakToeTr, PeakToeTr$z_score < 2)#removing outliers
PeakToeTr <- subset(PeakToeTr, PeakToeTr$z_score > -2)



# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
PeakToeTrMod <- brm(data = PeakToeTr, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)

```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

## UH

p <- withinSubPlotAvg(PeakToeUH, colName = 'maxmaxToes', dir = 'lower')
p + ylab('Peak Toe Pressure (kPa)')

extractVals(PeakToeUH, PeakToeUHMod, otherConfigs, baseline, 'maxmaxToes', 'lower')

## DH

p <- withinSubPlotAvg(PeakToeDH, colName = 'maxmaxToes', dir = 'lower')
p + ylab('Peak Toe Pressure (kPa)')

extractVals(PeakToeDH, PeakToeDHMod, otherConfigs, baseline, 'maxmaxToes', 'lower')

## trail

p <- withinSubPlotAvg(PeakToeTr, colName = 'maxmaxToes', dir = 'lower')
p + ylab('Peak Toe Pressure (kPa)')

extractVals(PeakToeTr, PeakToeTrMod, otherConfigs, baseline, 'maxmaxToes', 'lower')

```

## **Task Efficiency: Rate of Force Development (higher is better) - Weighted Lunge**

```{r}
#| echo: false
#| warning: false
#| include: false


###### Rate of Force Development
RFDSUDat <- SUDat %>% 
  group_by(Subject) %>%
  filter(RFD < 20000) %>%
  mutate(z_score = scale(RFD)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = RFDSUDat, aes(x = RFD, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

RFDSUDat <- subset(RFDSUDat, RFDSUDat$z_score < 2)#removing outliers
RFDSUDat <- subset(RFDSUDat, RFDSUDat$z_score > -2)



RFDSUDatMod <- brm(data = RFDSUDat, 
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)

```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 


p <- withinSubPlotAvg(RFDSUDat, colName = 'RFD', dir = 'higher')
p + ylab('Force Development (N/s)')

extractVals(RFDSUDat, RFDSUDatMod, otherConfigs, baseline, 'RFD', 'higher')
```

## **Balance: Center-of-Pressure Excursion (lower is better) - Weighted Lunge**

```{r}
#| echo: false
#| warning: false
#| include: false


###### COP Excursion
COPSUDat <- SUDat %>% 
  group_by(Subject) %>%
  mutate(z_score = scale(COPEx)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = COPSUDat, aes(x = COPEx, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

COPSUDat <- subset(COPSUDat, COPSUDat$z_score < 2)#removing outliers
COPSUDat <- subset(COPSUDat, COPSUDat$z_score > -2)



COPSUDatMod <- brm(data = COPSUDat, 
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)

```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 


p <- withinSubPlotAvg(COPSUDat, colName = 'COPEx', dir = 'lower')
p + ylab('Center-of-Pressure Excursion (m)')


extractVals(COPSUDat, COPSUDatMod, otherConfigs, baseline, 'COPEx', 'lower')

```

```{r}
#| echo: false
#| warning: false
#| include: false


treadmill_UH <- subset(TreadDat , TreadDat$Slope == '10')
# Level
#organizing data - grouping by subject and config by the variable being observed
psCOM_UH <- treadmill_UH %>% 
  group_by(Subject) %>%
  filter(COMWork_pos > 30) %>%
  mutate(z_score = scale(COMWork_pos))%>%
  group_by(Config) 

psCOM_UH <- subset(psCOM_UH, psCOM_UH$z_score > -2)
psCOM_UH <- subset(psCOM_UH, psCOM_UH$z_score < 2)

#Normalization histograms, Check for normalish distribution/outliers
ggplot(data = psCOM_UH, aes(x = COMWork_pos, fill = Config)) + geom_histogram() + facet_wrap(~Subject) 


## Bayes model 
# This model takes a while to run and may  crash your session 
#Wait until you receive a warning about rtools to run anything else
psCOM_UH_mod <- brm(data = psCOM_UH, 
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(psCOM_UH, colName = 'COMWork_pos', dir = 'lower')
p + ylab('Positive COM - Uphill (J)')


extractVals(psCOM_UH, psCOM_UH_mod, otherConfigs, baseline, 'COMWork_pos', 'lower')
```

```{r}
#| echo: false
#| warning: false
#| include: false

treadmill_DH <- subset(TreadDat, TreadDat$Slope == '-10')
# Level
#organizing data - grouping by subject and config by the variable being observed
ngCOM_DH <- treadmill_DH  %>% 
  group_by(Subject) %>%
  # filter(COMWork_pos > 30) %>%
  mutate(z_score = scale(COMWork_neg))%>%
  group_by(Config) 


ngCOM_DH <- subset(ngCOM_DH, ngCOM_DH$z_score > -2)
ngCOM_DH <- subset(ngCOM_DH, ngCOM_DH$z_score < 2)

#Normalization histograms, Check for normalish distribution/outliers
ggplot(data = ngCOM_DH, aes(x = COMWork_neg, fill = Config)) + geom_histogram() + facet_wrap(~Subject) 


## Bayes model 
# This model takes a while to run and may  crash your session 
#Wait until you receive a warning about rtools to run anything else
ngCOM_DH_mod <- brm(data = ngCOM_DH , 
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)
```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(ngCOM_DH, colName = 'COMWork_neg', dir = 'higher')
p + ylab('Negative COM - Downhill (J)')


extractVals(ngCOM_DH, ngCOM_DH_mod, otherConfigs, baseline, 'COMWork_neg', 'higher')
```

# Stability & Control

## **Ankle Stability: Peak Eversion Velocity (lower is better) - Uneven Terrain Walking**

```{r}
#| echo: false
#| warning: false
#| include: false


###### Peak eversion velocity

Everdat <- IMUdat %>% 
  group_by(Subject) %>%
  filter(pIEgyro > 0) %>%
  mutate(z_score = scale(pIEgyro)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = Everdat, aes(x = pIEgyro, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

Everdat <- subset(Everdat, Everdat$z_score < 2)#removing outliers
Everdat <- subset(Everdat, Everdat$z_score > -2)



EverdatMod <- brm(data = Everdat, # Bayes model
              family = gaussian,
              z_score ~ Config + imuSpeed + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 100, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(Everdat, colName = 'pIEgyro', dir = 'lower')
p + ylab('Eversion Velocity (deg/s)')

extractVals(Everdat, EverdatMod, otherConfigs, baseline, 'pIEgyro', 'lower')
```

## **Knee Joint Loading: Knee Abduction Moment (lower magnitude is better) - Weighted Lunge**

```{r}
#| echo: false
#| warning: false
#| include: false



### SU Knee Abduction Moment
KABDSUDat <- SUDat %>% 
  group_by(Subject) %>%
  filter(RkneeABDMom > -500, RkneeABDMom < 0) %>%
  mutate(z_score = scale(RkneeABDMom)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = KABDSUDat, aes(x = RkneeABDMom, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

KABDSUDat <- subset(KABDSUDat, KABDSUDat$z_score < 2)#removing outliers
KABDSUDat <- subset(KABDSUDat, KABDSUDat$z_score > -2)

KABDSUDat <- KABDSUDat %>%
  filter(Subject != 'ChadPrichard'& Subject != 'WesWeber')


KABDSUDatMod <- brm(data = KABDSUDat, 
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


### SU Knee Adduction Moment
# KADDSUDat <- SUDat %>% 
#   group_by(Subject) %>%
#   filter(RkneeADDMom < 500, RkneeADDMom > 0) %>%
#   mutate(z_score = scale(RkneeABDMom)) %>% 
#   group_by(Config)
# 
# # Look at histogram of the data if any outliers need to be removed
# ggplot(data = KADDSUDat, aes(x = RkneeADDMom, color = Config)) + geom_histogram() + facet_wrap(~Subject)
# 
# p <- withinSubPlot(KADDSUDat, colName = 'RkneeADDMom', dir = 'lower')
# p + ylab('Knee Adduction Moment (Nm)')
# 
# KADDSUDatMod <- brm(data = KADDSUDat, 
#               family = gaussian,
#               z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
#               prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
#                         prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
#                         prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
#                         prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
#               iter = 2000, warmup = 1000, chains = 4, cores = 4,
#               control = list(adapt_delta = .975, max_treedepth = 20),
#               seed = 190831)
# 
# extractVals(KADDSUDat, KADDSUDatMod, otherConfigs, baseline, 'RkneeADDMom', 'lower')

```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(KABDSUDat, colName = 'RkneeABDMom', dir = 'higher')
p + ylab('Knee Abduction Moment (Nm)')

extractVals(KABDSUDat, KABDSUDatMod, otherConfigs, baseline, 'RkneeABDMom', 'higher')
```

```{r}
#| echo: false
#| warning: false
#| include: false


# ### SU Ankle Inversion Moment
# AIMSUDat <- SUDat %>% 
#   group_by(Subject) %>%
#   filter(RankleInMom != 'NA', RankleInMom > 0) %>%
#   mutate(z_score = scale(RankleInMom)) %>% 
#   group_by(Config)
# 
# # Look at histogram of the data if any outliers need to be removed
# ggplot(data = AIMSUDat, aes(x = RankleInMom, color = Config)) + geom_histogram() + facet_wrap(~Subject)
# 
# p <- withinSubPlot(AIMSUDat, colName = 'RankleInMom', dir = 'lower')
# p + ylab('Ankle Inversion Moment (Nm)')
# 
# AIMSUDatMod <- brm(data = AIMSUDat, 
#               family = gaussian,
#               z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
#               prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
#                         prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
#                         prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
#                         prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
#               iter = 2000, warmup = 1000, chains = 4, cores = 4,
#               control = list(adapt_delta = .975, max_treedepth = 20),
#               seed = 190831)
# 
# extractVals(AIMSUDat, AIMSUDatMod, otherConfigs, baseline, 'RankleInMom', 'lower')

```

## **Ankle Stability: Ankle Eversion Moment (lower magnitude is better) - Weighted Lunge**

```{r}
#| echo: false
#| warning: false
#| include: false


### SU Ankle Eversion Moment
AEMSUDat <- SUDat %>% 
  group_by(Subject) %>%
  filter(RankleEvMom != 'NA', RankleEvMom < 0) %>%
  mutate(z_score = scale(RankleEvMom)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = AEMSUDat, aes(x = RankleEvMom, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

AEMSUDat <- subset(AEMSUDat, AEMSUDat$z_score < 2)#removing outliers
AEMSUDat <- subset(AEMSUDat, AEMSUDat$z_score > -2)



AEMSUDatMod <- brm(data = AEMSUDat, 
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)

extractVals(AEMSUDat, AEMSUDatMod, otherConfigs, baseline, 'RankleEvMom', 'higher')
```

```{r}
#| echo: false
#| warning: false
#| include: true 
#| layout-ncol: 2 

p <- withinSubPlotAvg(AEMSUDat, colName = 'RankleEvMom', dir = 'higher')
p + ylab('Ankle Eversion Moment (Nm)')

extractVals(AEMSUDat, AEMSUDatMod, otherConfigs, baseline, 'RankleEvMom', 'higher')

```

## **Stability (faster is better) - Landing on Uneven Terrain**

```{r}
#| echo: false
#| warning: false
#| include: false


### Trail stabilization time
TimeUnLandDat <- UnLandDat %>% 
  group_by(Subject) %>%
  mutate(z_score = scale(StabTime)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = TimeUnLandDat, aes(x = StabTime, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

TimeUnLandDat <- subset(TimeUnLandDat, TimeUnLandDat$z_score < 2)#removing outliers
TimeUnLandDat <- subset(TimeUnLandDat, TimeUnLandDat$z_score > -2)



TimeUnLandDatMod <- brm(data = TimeUnLandDat, 
              family = gaussian,
              z_score ~ Config + Order + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 


p <- withinSubPlotAvg(TimeUnLandDat, colName = 'StabTime', dir = 'lower')
p + ylab('Stabilization Time (s)')

extractVals(TimeUnLandDat, TimeUnLandDatMod, otherConfigs, baseline, 'StabTime', 'lower')
```

# Quantitative Fit

## **Heel Hold: Heel contact area (higher is better) - Uneven Terrain Walking**

```{r}
#| echo: false
#| warning: false
#| include: false



###### Heel Contact  all tasks

HeelCondat <- PressWalkDat %>% 
  group_by(Subject) %>%
  mutate(z_score = scale(heelAreaP)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = HeelCondat, aes(x = heelAreaP, fill = Movement)) + geom_histogram() + facet_wrap(~Subject)

HeelCondat <- subset(HeelCondat, HeelCondat$z_score < 2)#removing outliers
HeelCondat <- subset(HeelCondat, HeelCondat$z_score > -2)

p <- withinSubPlotAvg(HeelCondat, colName = 'heelAreaP', dir = 'higher')
p + ylab('Heel Contact (%)')

# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
HeelCondatMod <- brm(data = HeelCondat, # Bayes model
              family = gaussian,
              z_score ~ Config + Movement + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)

extractVals(HeelCondat, HeelCondatMod, otherConfigs, baseline, 'heelAreaP', 'higher')
```

```{r}
#| echo: false
#| warning: false
#| include: false
#| layout-ncol: 2 

###### Heel Contact by task

DHCondat <- PressWalkDat %>% 
  group_by(Subject) %>%
  filter(Movement == 'dh')%>%
  mutate(z_score = scale(heelAreaP)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = DHCondat, aes(x = heelAreaP, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

DHCondat <- subset(DHCondat, DHCondat$z_score < 2)#removing outliers
DHCondat <- subset(DHCondat, DHCondat$z_score > -2)

# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
DHCondatMod <- brm(data = DHCondat, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)



UHCondat <- PressWalkDat %>% 
  group_by(Subject) %>%
  filter(Movement == 'uh')%>%
  mutate(z_score = scale(heelAreaP)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = UHCondat, aes(x = heelAreaP, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

UHCondat <- subset(UHCondat, UHCondat$z_score < 2)#removing outliers
UHCondat <- subset(UHCondat, UHCondat$z_score > -2)

# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
UHCondatMod <- brm(data = UHCondat, # Bayes model
              family = gaussian,
              z_score ~ Config + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)


TCondat <- PressWalkDat %>% 
  group_by(Subject) %>%
  filter(Movement == 'trailwalk' | Movement == 'trail')%>%
  mutate(z_score = scale(heelAreaP)) %>% 
  group_by(Config)

# Look at histogram of the data if any outliers need to be removed
ggplot(data = TCondat, aes(x = heelAreaP, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

TCondat <- subset(TCondat, TCondat$z_score < 2)#removing outliers
TCondat <- subset(TCondat, TCondat$z_score > -2)

# Note for trail run metrics: Warmup was reduced (from 1000 to 500)
TCondatMod <- brm(data = TCondat, # Bayes model
              family = gaussian,
              z_score ~ Config  + (1 + Config| Subject), #fixed effect of configuration and time period with a different intercept and slope for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)
```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(DHCondat, colName = 'heelAreaP', dir = 'higher')
p + ylab('Downhill - Heel Contact (%)')

extractVals(DHCondat, DHCondatMod, otherConfigs, baseline, 'heelAreaP', 'higher')

p <- withinSubPlotAvg(UHCondat, colName = 'heelAreaP', dir = 'higher')
p + ylab('Uphill - Heel Contact (%)')

extractVals(UHCondat, UHCondatMod, otherConfigs, baseline, 'heelAreaP', 'higher')

p <- withinSubPlotAvg(TCondat, colName = 'heelAreaP', dir = 'higher')
p + ylab('Trail - Heel Contact (%)')

extractVals(TCondat, TCondatMod, otherConfigs, baseline, 'heelAreaP', 'higher')
```

```{r}
#| echo: false
#| warning: false
#| include: false

#Static dorsal pressure

Static <- subset(staticPress, staticPress$Movement == 'Standing')


peakDorsal <- Static%>% 
  group_by(Subject) %>%
  mutate(z_score = scale(maxDorsalPressure)) %>% 
  group_by(Config)

ggplot(data = peakDorsal, aes(x = maxDorsalPressure, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

# peakDorsal  <- subset(peakDorsal , peakDorsal $z_score < 2) #remov. outliers
# peakDorsal  <- subset(peakDorsal , peakDorsal $z_score > -2)


DorsalMaxMod <- brm(data = peakDorsal, # Bayes model
              family = gaussian,
              z_score ~ Config + (1|Subject), #fixed effect of configuration  with different intercept each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained 
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)





```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(peakDorsal, colName = 'maxDorsalPressure', dir = 'lower')
p + ylab('Max Dorsal Pressure (kPa)') 



extractVals(peakDorsal, DorsalMaxMod, otherConfigs, baseline, 'maxDorsalPressure', 'lower')
```

```{r}
#| echo: false
#| warning: false
#| include: false


###### peak dorsal pressure 

Static <- subset(staticPress, staticPress$Movement == 'Standing')


avgDorsal <- Static%>% 
  group_by(Subject) %>%
  mutate(z_score = scale(meanDorsalPressure)) %>% 
  group_by(Config)

ggplot(data = avgDorsal, aes(x = meanDorsalPressure, fill = Config)) + geom_histogram() + facet_wrap(~Subject)

# peakDorsal  <- subset(peakDorsal , peakDorsal $z_score < 2) #remov. outliers
# peakDorsal  <- subset(peakDorsal , peakDorsal $z_score > -2)


DorsalMeanMod <- brm(data = avgDorsal, # Bayes model
              family = gaussian,
              z_score ~ Config + (1|Subject), #fixed effect of configuration with a different intercept for each subject
              prior = c(prior(normal(0, 1), class = Intercept), #The intercept prior is set as a mean of 25 with an SD of 5 This may be interpreted as the average loading rate (but average is again modified by the subject-specific betas)
                        prior(normal(0, 1), class = b), #beta for the intercept for the change in loading rate for each configuration
                        prior(cauchy(0, 1), class = sd), #This is a regularizing prior, meaning we will allow the SD of the betas to vary across subjects
                        prior(cauchy(0, 1), class = sigma)), #overall variability that is left unexplained
              iter = 2000, warmup = 1000, chains = 4, cores = 4,
              control = list(adapt_delta = .975, max_treedepth = 20),
              seed = 190831)




```

```{r}
#| echo: false
#| warning: false
#| include: true
#| layout-ncol: 2 

p <- withinSubPlotAvg(avgDorsal, colName = 'meanDorsalPressure', dir = 'higher')
p + ylab('Mean Dorsal Pressure (kPa)') 

extractVals(avgDorsal, DorsalMeanMod, otherConfigs, baseline, 'meanDorsalPressure', 'higher')

```
