---
title: "EHRunKineticsKinematics"
author: "Dan Feeney"
date: "4/20/2021"
output: html_document
---

# End and Health Validation analyses

## Sex: (1) Male, (2) Female
## Shoe: (1) DD, (2) SD, (3) SL (Laces)

```{r message=FALSE, warning=FALSE}
rm(list=ls())
library(readxl)
library(tidyverse)
library(emmeans)
library(lme4)


dat <- suppressWarnings(read_xlsx(file.choose()))
#Making variables factors or numeric
dat$Subject <- as.factor(dat$Subject)
dat$Sex <- as.factor(dat$Sex)
dat$Period <- as.factor(dat$Period)
dat$Condition <- as.factor(dat$Condition)
dat$`Knee Max Angle X` <- as.numeric(dat$`Knee Max Angle X`)
dat$`Knee Max Angle Y` <- as.numeric(dat$`Knee Max Angle Y`) 
dat$`Knee Max Angle Z` <- as.numeric(dat$`Knee Max Angle Z`) 
dat$`Knee Max Power` <- as.numeric(dat$`Knee Max Power`) / dat$Mass
dat$`Knee Min Angle X` <- as.numeric(dat$`Knee Min Angle X`)
dat$`Knee Min Angle Y` <- as.numeric(dat$`Knee Min Angle Y`)
dat$`Knee Min Angle Z` <- as.numeric(dat$`Knee Min Angle Z`)
dat$`Knee Max Moment X` <- as.numeric(dat$`Knee Max Moment X`) / dat$Mass
dat$`Knee Max Moment Y` <- as.numeric(dat$`Knee Max Moment Y`) / dat$Mass
dat$`Knee Max Moment Z` <- as.numeric(dat$`Knee Max Moment Z`) / dat$Mass
dat$`Knee Min Power` <- as.numeric(dat$`Knee Min Power`) / dat$Mass
dat$`Knee Negative Work` <- as.numeric(dat$`Knee Negative Work`) / dat$Mass
dat$`Knee Positive Work` <- as.numeric(dat$`Knee Positive Work`) / dat$Mass
dat$`Knee ROM X` <- as.numeric(dat$`Knee ROM X`)
dat$`Knee ROM Y` <- as.numeric(dat$`Knee ROM Y`)
dat$`Knee ROM Z` <- as.numeric(dat$`Knee ROM Z`)
dat$`Knee Min Moment X` <- as.numeric(dat$`Knee Min Moment X`) / dat$Mass
dat$`Knee Min Moment Y` <- as.numeric(dat$`Knee Min Moment Y`) / dat$Mass


dat$`Hip Max Angle X` <- as.numeric(dat$`Hip Max Angle X`)
dat$`Hip Max Angle Y` <- as.numeric(dat$`Hip Max Angle Y`)
dat$`Hip Max Angle Z` <- as.numeric(dat$`Hip Max Angle Z`)
dat$`Hip Max Moment X` <- as.numeric(dat$`Hip Max Moment X`) / dat$Mass
dat$`Hip Max Moment Y` <- as.numeric(dat$`Hip Max Moment Y`) / dat$Mass
dat$`Hip Max Moment Z` <- as.numeric(dat$`Hip Max Moment Z`) / dat$Mass
dat$`Hip Max Power` <- as.numeric(dat$`Hip Max Power`) / dat$Mass
dat$`Hip Negative Work` <- as.numeric(dat$`Hip Negative Work`) / dat$Mass
dat$`Hip Positive Work` <- as.numeric(dat$`Hip Positive Work`) / dat$Mass
dat$`Hip ROM X` <- as.numeric(dat$`Hip ROM X`)
dat$`Hip ROM Y` <- as.numeric(dat$`Hip ROM Y`)
dat$`Hip ROM Z` <- as.numeric(dat$`Hip ROM Z`)

```

## Use very generic outlier removal for all of the non-physiological values
```{r}
remove_outliers <- function(x, na.rm = TRUE, ...) {
  mn <- median(x, na.rm = TRUE)
  std <- IQR(x, na.rm = TRUE)
  y <- x
  y[x < (mn - 1.96*std)] <- NA
  y[x > (mn + 1.96*std)] <- NA
  y
}

cleanedDat <- dat %>%
  group_by(Subject) %>%
  mutate(
    KneeAngX = remove_outliers(`Knee Max Angle X`),
    KneeAngY = remove_outliers(`Knee Max Angle Y`),
    KneeAngZ = remove_outliers(`Knee Max Angle Z`),
    KneeMomX = remove_outliers(`Knee Max Moment X`),
    KneePosMomY = remove_outliers(`Knee Max Moment Y`),
    KneeNegMomY = remove_outliers(`Knee Min Moment Y`),
    KneeMomZ = remove_outliers(`Knee Max Moment Z`),
    NegFootWork = remove_outliers(`Distal Foot Negative Work`),
    PosFootWork = remove_outliers(`Distal Foot Positive Work`),
    NegAnkleWork = remove_outliers(`Ankle Negative Work`),
    PosAnkleWork = remove_outliers(`Ankle Positive Work`),
    AnkleAngX = remove_outliers(`Ankle Max Angle X`),
    AnkleAngY = remove_outliers(`Ankle Max Angle Y`),
    AnkleAngZ = remove_outliers(`Ankle Max Angle Z`),
    AnkleMomX = remove_outliers(`Ankle Max Moment X`),
    AnkleMomY = remove_outliers(`Ankle Max Moment Y`),
    AnkleMomZ = remove_outliers(`Ankle Max Moment Z`)
  )

summary(cleanedDat$NegFootWork)

```

## Make function to plot data and second to run lmer. These are the helper functions used below
```{r}

plotAndStore <- function(col, dfName){
  
  genPlot <- ggplot(data = dfName, mapping = aes(x = .data[[col]], fill = dfName$Condition)) +
    geom_density() +   facet_wrap(~dfName$Subject) +     
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle(col) +
    guides(fill=guide_legend(title="Configuration"))
  
  return(genPlot)
}


plotAndStore('NegFootWork', cleanedDat)

testAnova <- function(metric, df) {
  
  myformula <- as.formula(paste0(metric," ~ Condition", "+ Period"," + (1|Subject)"))
  myformula2 <- as.formula(paste0(metric, " ~ Period", " + (1|Subject)"))
  
  full.mod = lmer(myformula, data = df, REML = TRUE, na.action = "na.omit" )
  red.mod = lmer(myformula2, data = df, REML = TRUE, na.action = "na.omit" )
  
conditions.emm <- emmeans(full.mod, "Condition", lmer.df = "satterthwaite")
#conditions.emm
contrast(conditions.emm, "trt.vs.ctrl", ref = "3") 


  newList <- list("randEffectMod" = summary(full.mod), "anovaBetweenMods" = anova(full.mod, red.mod),
                  "contrasts" = conditions.emm, "Contrasts2" = contrast(conditions.emm, "trt.vs.ctrl", ref = "3"))
  return(newList)
  
}

testAnova('NegFootWork',cleanedDat)


```



## Look at knee abduction, abduction moment, internal rotation
###  Y points left on each joint from the left leg, so a positive Knee moment in Y would be flexion. X points inferior for the hip and knee but forward (sagittal)  on the foot leaving Z to point sagittal on the hip and knee but superior on the foot.

## Hypotheses: a.	BOA configurations will reduce peak knee abduction b.	BOA will reduce peak knee adduction moment (internal) c.	BOA configurations will reduce peak knee internal rotation


## Negative foot work
```{r}
# Subset for distal foot work that is reasonable
# all neg foot work should be less than 50 based on literature
plotAndStore('NegFootWork',cleanedDat)
testAnova('NegFootWork',cleanedDat)


```

## Positive foot work
```{r}
# Positive foot work
plotAndStore('PosFootWork',cleanedDat)

testAnova('PosFootWork',cleanedDat)

```

## Ankle powers and work
```{r}
plotAndStore('NegAnkleWork',cleanedDat)

testAnova('NegAnkleWork',cleanedDat)
```

## Ankle positive work
```{r}
plotAndStore('PosAnkleWork',cleanedDat)

testAnova('PosAnkleWork', cleanedDat)
```
## Knee angles



## Knee X moment. There may still be some high values but data look mostly clean
```{r}
plotAndStore('KneeMomX',cleanedDat)

testAnova('KneeMomX', cleanedDat)
```

## Knee Y moments
```{r}
plotAndStore('KneePosMomY',cleanedDat)
testAnova('KneePosMomY', cleanedDat)

plotAndStore('KneeNegMomY', cleanedDat)
testAnova('KneeNegMomY', cleanedDat)

```


## Knee Z moments
```{r}
plotAndStore('KneeMomZ',cleanedDat)
testAnova('KneeMomZ', cleanedDat)


```

## Ankle angles
```{r}
plotAndStore('AnkleAngX', cleanedDat)
plotAndStore('AnkleAngY', cleanedDat)
plotAndStore('AnkleAngZ', cleanedDat)

```

## Ankle moments
```{r}
summary(cleanedDat$AnkleMomX) #ab/adduction moment?
summary(cleanedDat$AnkleMomY) #flexion/extension moment
summary(cleanedDat$AnkleMomZ) #internal rotation moment?


plotAndStore('AnkleMomX', cleanedDat)


```


